---
title: "qview_intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{qview_intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qview)
```

Introduction
The qview package provides a quick and easy way to summarize and visualize your data. It is designed to offer a concise overview of a data frame, including summary statistics and distribution plots for numeric columns.

Installation
You can install the qview package from GitHub using the following command:

```{r}
# Install remotes if you haven't already
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}

# Install qview from GitHub
remotes::install_github("LukasAldini/qview")
```

Usage
Loading the Library
First, load the qview library:

```{r}
library(qview)
```

Example Data
Let's create an example data frame to demonstrate the functions:

```{r}
set.seed(123)
df <- data.frame(
  a = rnorm(100),
  b = rnorm(100),
  c = rnorm(100)
)
head(df)
```

Summarizing the Data
Use the summarize_data function to get summary statistics for the numeric columns:

```{r}
summary_df <- summarize_data(df)
print(summary_df)
```

Plotting the Distribution
Use the plot_distribution function to create histograms and boxplots for numeric columns:

```{r}
plots <- plot_distribution(df)

# Display the plots for column 'a'
print(plots$a$histogram)
print(plots$a$boxplot)
```

Quick View of the Data
Use the qview function to get both the summary and the plots in a single call:

```{r}
result <- qview(df)

# Summary statistics
print(result$summary)

# Distribution plots
print(result$plots$a$histogram)
print(result$plots$a$boxplot)
print(result$plots$b$histogram)
print(result$plots$b$boxplot)
print(result$plots$c$histogram)
print(result$plots$c$boxplot)
```

Conclusion
The qview package is a simple and effective tool for quickly summarizing and visualizing data frames. With just a few lines of code, you can gain insights into the distribution and key statistics of your data.
